{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-09 Paper/main.tex
Simul

	\subsubsection{Functional Principal Component Regression}
	The model used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}. In addition to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated Eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function. But since the FPCR is ultimately estimated with a linear model with the corresponding scores as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $L$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$. As will be described, it seems that neither a convex behavior of the MSPE nor any clear relationship can be observed between the number of basis functions and the number of FPC's. This might be because the dependency {\color{red} Reformulate this in the meeting!!!} (FPCA is performed on the smoothed curves) is too complex to draw conclusions regarding this within this simulation study. Therefore, we will limit ourselves to a brief description. In this simulation, the cross-validated choice of basis functions indicates that the FPCR might not take the differing signal-to-noise ratios of the responses into account (same number of basis functions for the different signal-to-noise ratios). A possible explanation might be that the FPC's, which affect the relevant degrees of freedom, are solely calculated from the smoothed curves, not considering the noise in the responses.

@@

	This convex behavior was not observed for the FPCR where no clear relationship between the basis functions and the number of FPC could be uncovered. A hypothesis for this is that the dependency between the truncation parameter $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is too complex to capture in our setting. To examine this further, additional simulations ( Appendix \ref{Tables_sim_additional}) were conducted for B-spline basis functions with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$. As in the simulation study, we can find potential signs of overfitting for all setups and both choices of $L$. The additional simulations revealed evidence that there might exist a relationship from $n_{FPC} = 3$ onwards: For $n_{FPC} \in \{3, \dots, 7 \}$, the 10-fold cross-validated MSPE is always lower for 50 than for 70 basis functions which might be the first sign of an $L$ that is chosen too large and subsequent undersmoothing. Following this, it seems that once a sufficient number of basis functions is used to expand the curves, the FPCR performs better using a more conservative number of basis functions (here $L = 50$). The settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions compared to the main simulation, while $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance than in the main simulation study, although the signal-to-noise ratios of the responses are not affecting the construction of the FPC's. This might indicate beneficial attributes of a lower truncation parameter in settings with low signal-to-noise responses.

	%Keeping \cite{Jolliffe_1982} in mind, we ....(refer to problematic of missing insights in pysics / chemistry?)

>>>>

	\subsubsection{Functional Principal Component Regression}
	The model used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}. In addition to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated Eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function. {\color{orange} The selection of the truncation parameter $L$ is difficult since the approximated Eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function. In addition, the choice of the number of FPC's adds to the complexity of the model since some eigenfunctions, which hold important traits, corresponding to lower variances would be omitted for the model as described in 3.1.} But since the FPCR is ultimately estimated with a linear model with the corresponding scores as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $L$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$. As will be described, it seems that neither a convex behavior of the MSPE nor any clear relationship can be observed between the number of basis functions and the number of FPC's. This might be because the dependency {\color{red} Reformulate this in the meeting!!!} (FPCA is performed on the smoothed curves) is too complex to draw conclusions regarding this within this simulation study. Therefore, we will limit ourselves to a brief description. In this simulation, the cross-validated choice of basis functions indicates that the FPCR might not take the differing signal-to-noise ratios of the responses into account (same number of basis functions for the different signal-to-noise ratios). A possible explanation might be that the FPC's, which affect the relevant degrees of freedom, are solely calculated from the smoothed curves, not considering the noise in the responses.

@@

	This convex behavior was not observed for the FPCR where no clear relationship between the basis functions and the number of FPC could be uncovered. A hypothesis for this is that the dependency between the truncation parameter $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is too complex to capture in our setting. {\color{orange}redundant?} To examine this {\color{orange} unclear relationship between the basis functions and the number of FPC} further, additional simulations (Appendix \ref{Tables_sim_additional}) were conducted for B-spline basis functions with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$. As in the simulation study, we can find potential signs of overfitting for all setups and both choices of $L$. The additional simulations revealed evidence that there might exist a relationship from $n_{FPC} = 3$ onwards: For $n_{FPC} \in \{3, \dots, 7 \}$, the ten-fold cross-validated MSPE is always lower for 50 than for 70 basis functions which might be the first sign of an $L$ that is chosen too large and subsequent undersmoothing. Following this, it seems that once a sufficient number of basis functions is used to expand the curves, the FPCR performs better using a more conservative number of basis functions (here $L = 50$). The settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions compared to the main simulation, while $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance than in the main simulation study, although the signal-to-noise ratios of the responses are not affecting the construction of the FPC's {\color{orange} we cannot compare the Y1 by the number of basis functions since we don't have the results of n=5,6,7. and I don't get the although part. The regressors are influenced by the noise so the fact fpc is not affected would not be important? How about putting 'The results of FPCR is relatively more stable thn basis expansion regression regarding the number of basis function. It seems like that the number of FPC's is rather significant.'}. This might indicate beneficial attributes of a lower truncation parameter in settings with low signal-to-noise responses.
	%Keeping \cite{Jolliffe_1982} in mind, we ....(refer to problematic of missing insights in pysics / chemistry?)
